% From mitthesis package
% Version: 1.04, 2023/10/19
% Documentation: https://ctan.org/pkg/mitthesis


\chapter{Results, Analysis and Evaluation}

% Introduction
% Describe your methodology: provide details
% Present your results
% Discuss your findings
% Address limitations
% Relate back to literature review
% Explain your experiments
% Assessment of experiments
% End result: software itself
% Conclude with implications of future work

\section{Results and Analysis}

% * This chapter is relevant to projects where experiments or simulations were carried out with the code written.
% 1. Why were certain experiments carried out but not others?
% 2. What were the important parameters in the simulation and how did they affect the results?
% 3. Verify the accuracy and completeness of the data presented in reports.
    
% * If there are many graphs and tables associated with this chapter they may be put in an appendix, but it is generally 
% better to keep these close to the text they illustrate, as this is easier for the reader.

\section{Achievement of Objectives}

\subsection{Develop and deploy smart sensors to monitor energy consumption, water usage and temperature}

This objective was successfully achieved. Energy, water flow, and temperature sensors were installed in a real AirBnB 
property. Figure \ref{fig:ac-power} illustrates the activation of the air conditioning, Figure 
\ref{fig:shower-water-flow} depicts the water flow during a shower, and Figure \ref{fig:ac-temperature} presents a 
24-hour temperature graph.

\subsection{Build an application programming Interface (API) to facilitate access to sensor-collected data}

This aim was effectively fulfilled. An API was developed to provide access to the data collected by the sensors. The API
adheres to OpenAPI standards and is documented using Swagger. Figure \ref{fig:swagger} displays the API documentation.

\subsection{Design and generate comprehensive daily and end-of-stay reports for guests}

The intended goal was reached. Daily and end-of-stay reports can be generated for guests, containing information on 
energy consumption, water usage, and temperature. Figure \ref{fig:whatsapp-daily-report} shows a sample daily report, 
while Figure \ref{fig:whatsapp-final-report} presents a sample end-of-stay report.

\subsection{Create a user-friendly web application for hosts to monitor and manage their property's resource consumption}

The desired outcome was accomplished. A web application was developed for hosts to monitor and manage their property's 
resource consumption. Section \ref{sec:user-interface} of the methodology chapter provides wireframes for the web 
application.

\section{Achievement of Requirements}

% * A description of the test plan, i.e., how the program/system was verified.

% * Put the actual test results in an appendix if too long. This section may also include a user evaluation based on 
% feedback where appropriate.

The system testing approach adhered to Test-Driven Development (TDD) principles, which involved writing tests prior to 
implementing the corresponding functionality. Tests were created in a bottom-up manner, beginning with hardware testing 
and progressing through the system layers. These tests were integrated into Continuous Integration (CI) pipelines using 
GitHub Actions \cite{GitHub2024} to ensure that tests were executed automatically whenever changes were made to the 
codebase.

\subsection{Hardware Testing}

Two types of tests were conducted on the hardware components: calibration and response time. Calibration tests involved 
comparing sensor readings with those obtained from standard instruments, including multimeters, graduated cylinders, and
thermometers. Response time tests measured the duration required for the sensors to react to environmental changes, 
ensuring that they could accurately capture real-time variations, such as turning on an appliance, filling a glass of 
water, or opening a window.

\subsubsection{Current Sensors}

The sensors were connected to a power strip alongside a multimeter, while an induction stove and a kettle were used to 
create variations in current consumption. Table \ref{tab:current-sensors-calibration} presents the results of the 
calibration tests for the current sensors. Although the sensors effectively captured changes in current, there was a 
slight deviation from the readings obtained with the multimeter. The standard deviation was calculated to be less than 
0.1A, which falls within the acceptable range for the application. Figure \ref{fig:using-kettle-and-ac} illustrates the 
change in power consumption when the kettle was turned on (left), demonstrating the sensors' capability to capture rapid 
changes in current consumption.

\subsubsection{Water Flow Sensor}

Two distinct tests were performed on the water flow sensor. The first test involved connecting the sensor to a funnel 
and pouring one liter of water into a graduated cylinder at varying speeds: slow, medium, and fast. The second test 
aimed to capture changes in water flow when rapidly filling the cylinder. Table \ref{tab:water-flow-sensor-calibration}
shows the results of the first test, where an issue with slow water flow was identified due to the sensor's inability to 
detect changes at low speeds. Several improvements were made to the code, including separating the code into different 
tasks, to enhance accuracy; however, it was ultimately concluded that a higher-precision sensor was necessary, which 
could not be acquired in time for the project.

Figure \ref{fig:water-flow-sensor-response} demonstrates the response of the water flow sensor when filling the 
container, showing that the sensor could capture changes in water flow in less than 10 seconds, which is suitable for 
fast tasks like filling a glass. Any flow rate below this speed, such as a small stream from a faucet, may not be 
detected by the sensor.

\subsubsection{Temperature Sensors}

Testing the temperature sensors required two tests. The first involved comparing the sensors with a thermometer to 
evaluate the accuracy of the readings over 12 hours; the results were satisfactory, with a standard deviation of less 
than 0.5 degrees Celsius. The second test assessed the response time of the sensors by placing one sensor in a glass of 
ice and another in a glass of boiling water. Figure \ref{tab:temperature-sensors-calibration} presents the calibration 
test results for the temperature sensors.

Figure \ref{fig:temp-sensor-response} illustrates the temperature changes when the sensors were submerged. Once the 
temperature reached the maximum and minimum values, the sensors were swapped to check the response time, which was under 
a minute—acceptable for the application, as drastic temperature changes are not typical in indoor or outdoor settings.

\subsection{Back-end Testing}

A comprehensive set of tests was developed to evaluate the performance of the back-end system. The unit, integration, 
and system tests utilized the OpenAPI specification to verify the payloads and responses from the API, ensuring that the 
documentation aligned with the actual implementation. This approach required that any new feature added to the API 
necessitated an update to the Swagger documentation, establishing it as a single source of truth.

\subsubsection{Unit Testing}

Unit tests were developed for every endpoint and utility function in the API. Mocha and Chai were employed to write the 
tests in JavaScript, resulting in a total of 71 unit tests designed to assess payloads, responses, and error handling. 
Figure \ref{fig:api-unit-tests-results} displays the results of the tests conducted locally.

\subsubsection{Integration Testing}

Figure \ref{fig
} presents the results from the integration tests, which were utilized to verify the proper functioning of the different 
components of the API. For instance, a test creates a user, logs in, creates listings, modifies those listings, and 
finally deletes them along with the user. These tests were also developed using Mocha \cite{Mocha2024} and Chai 
\cite{Chai2024}.

\subsubsection{System Testing}

System tests were executed using Postman \cite{Postman2024} to evaluate the API as a whole, covering the entire workflow 
from user creation and login to provider registration, listing and reservation retrieval from AirBnB, simulating a stay, 
and finally fetching reports. An image depicting these tests can be found in Figure \ref{fig:systems-tests-results}.

\subsubsection{Regression Testing}

Unit and integration tests were automatically executed using GitHub Actions every time code was pushed to the 
repository. Notifications were sent via email if the code failed to compile or if any tests did not run successfully. 
Figure \ref{fig:api-build} illustrates a successful build of the API.

\subsection{Front-end Testing}

Testing of the User Interface was conducted manually during the development phase, followed by a small group of users 
(guests and hosts) testing the system and completing surveys to gather feedback on their experiences with the 
application.

\subsubsection{User Testing}

Due to the low season in the region where the AirBnB property is located, it was not feasible to gather a large number 
of users for testing. Ultimately, only four individuals participated in the testing: two guests and two hosts. Tables 
\ref{tab:hosts-survey-results} and \ref{tab:guests-survey-results} present the results of the surveys.

\section{Evaluation}

% * Evaluation and critical evaluation of the results including strong and weak points, lessons learnt, and design decisions.
% \begin{itemize}

% * Consider what you would do differently, are there ways in which the project could be improved or extended?

% Performance Evaluation: Evaluate the performance of your system. This could be in terms of speed, resource usage, or any other relevant metrics.
% User Feedback: If possible, gather feedback from users. This could be done through user testing, surveys, or interviews.
% Reflection: Reflect on the development process. What went well? What didn't? What would you do differently next time?

As mentioned in the first section of this chapter, the project objectives were successfully met, and the system is 
capable of performing all essential functionalities. Certain design decisions, such as adopting Test-Driven Development 
(TDD) and Continuous Integration (CI), were vital in delivering a robust solution, despite extending the development 
timeline. Regarding IoT device security, utilizing Rust \cite{Rust2024} would have been advantageous; however, due to 
limited experience with the language and the smaller ecosystem of sensor libraries, C++ and PlatformIO were selected 
instead.

Sensor calibration involved considerable trial and error, which should be taken into account for future projects, as it 
impacted the original schedule. Low-cost sensors were sourced locally due to budget and time constraints, but opting for 
more precise sensors, particularly for the water flow sensor, would have been preferable.

The decision to use JavaScript and Node.js for the API proved effective, as the development process was expedited by the 
extensive support for the language and the abundance of available libraries. The integration of Agenda for task 
scheduling was an excellent choice, given its compatibility with MongoDB and user-friendly nature. Incorporating OpenAPI 
and Swagger into the code and tests facilitated a more organic approach to documentation.

The User Interface was developed using low-code tools, a shift from the initial plan to use Flutter \cite{Flutter2024} 
or React \cite{React2024} due to time constraints. Appsmith demonstrated to be a fast and user-friendly tool, leveraging 
the power of JavaScript, and ultimately allowed for the implementation of all features within two weeks.

Finally, deploying the solution on Google Cloud was a strategic decision. Having a dedicated virtual machine available 
24/7 was crucial for storing data from the sensors. The use of Docker simplified development in both local and remote 
environments, enabling consistent container configurations across both setups.

\section{Limitations}

This project faced a few limitations that impacted its overall scope and effectiveness:

\begin{itemize}
    \item \textbf{Integration with Airbnb}: One of the most significant limitations was the inability to integrate the 
    system with Airbnb. Although the project aimed to pull listings and reservations from the platform, technical 
    challenges or restrictions in accessing Airbnb's API prevented this functionality from being realized. As a result, 
    this had to be simulated after capturing AirBnB's web application responses.
    \item \textbf{Limited User Testing}: The user testing phase was constrained by the low season in the region where 
    the AirBnB property is located. Ultimately, only four users participated in the testing: two guests and two hosts. 
    This limited sample size may not have adequately represented the broader user base, potentially skewing feedback and 
    insights. With a more diverse group of testers, the project could have benefited from a wider range of perspectives 
    and suggestions for improvement.
\end{itemize}