% From mitthesis package
% Version: 1.04, 2023/10/19
% Documentation: https://ctan.org/pkg/mitthesis


\chapter{Results, Analysis and Evaluation}

\section{Measuring Achievement of Objectives}

\subsection{Develop and deploy smart sensors to monitor energy consumption, water usage and temperature}

This objective was achieved. Energy, water flow and temperature sensors were installed in a real AirBnB property. 
Figure \ref{fig:ac-power} shows turning on a kettel to boil water, in figure \ref{fig:ac-temperature} the flow of 
water for filling up a glass is pictured and finally, a 24 hour temperature graph is shown in figure TODO: Z.

\subsection{Build an application programming Interface (API) to facilitate access to sensor-collected data}

This objective was achieved. An API was developed to provide access to the data collected by the sensors. The API
complies with OpenAPI standards and is documented using Swagger. Figure \ref{fig:swagger} shows the API documentation.

\subsection{Design and generate comprehensive daily and end-of-stay reports for guests}

This objective was achieved. Daily and end-of-stay reports can be generated for guests. The reports include information
on energy consumption, water usage and temperature. Figure \ref{fig:whatsapp-daily-report} shows a sample daily report 
and figure \ref{fig:whatsapp-final-report} shows a sample end-of-stay report.

\subsection{Create a user-friendly web application for hosts to monitor and manage ther property's resource consumption}

This objective was achieved. A web application was developed for hosts to monitor and manage their property's resource.
Section \ref{sec:user-interface} of the methodology chapter shows the wireframes for the web application.

\section{Measuring Achievement of Requirements}

\subsection{Testing}

% * A description of the test plan, i.e., how the program/system was verified.

% * Put the actual test results in an appendix if too long. This section may also include a user evaluation based on 
% feedback where appropriate.

The approach used to test the system was to follow Test-Driven Development (TDD) principles. This involved writing tests 
before writing the code to implement the functionality. Tests were written in a bottom-up fashion, starting with 
hardware testing and then moving up the system layers. The tests were integrared into Continous Integration (CI) 
pipelines using GitHub Actions \cite{GitHub2024} to ensure that the tests were run automatically whenever changes were 
made to the codebase.

A test plan was developed to evaluate the performance of the system. The plan included the following steps:

\section{Results and Analysis}

% * This chapter is relevant to projects where experiments or simulations were carried out with the code written.
% 1. Why were certain experiments carried out but not others?
% 2. What were the important parameters in the simulation and how did they affect the results?
% 3. Verify the accuracy and completeness of the data presented in reports.
    
% * If there are many graphs and tables associated with this chapter they may be put in an appendix, but it is generally 
% better to keep these close to the text they illustrate, as this is easier for the reader.

\subsection{Hardware Testing Results}

Two types of tests were carried out on the hardware components: calibration and response time. The calibration tests 
consisted of comparing the readings from the sensors with readings with off-the-shelf instruments such as multimeters,
a graduated cylenrder and a thermometer. The response time tests consisted of measuring the time it took for the sensors
to respond to changes in the environment, this was crucial to ensure that the sensors were able to capture changes in
real-time, for example, turning on an appliance, filling up a glass of water or opening a window.

\subsubsection{Current Sensors}

The sensors were connected to a power strip together with the multimeter, an induction stove and a kettle were used to
generate changes in current consumption. Table \ref{tab:current-sensors-calibration} shows the results of the 
calibration tests for the current sensors. While the sensors were able to capture changes in current, there was a small 
deviation from the readings obtained with the multimeter. The standard deviation was calculated to be less than 0.1A, 
which was within the acceptable range for the application. Figure \ref{fig:using-kettle-and-ac} shows the change in 
power consumption when turning on a kettel (left), the idea was to able to capture rapid change in current consumption 
and according to this image the sensors were able to do so.

\subsubsection{Water Flow Sensor}

Two different tests were conducted on the water flow sensor, first the sensor was connected to a funnel and a liter of
water was then poured into the graduated cylinder at different speeds: slow, medium and fast. The second test was to 
capture the change in water flow when filling up the cylinder at high speed. Table 
\ref{tab:water-flow-sensor-calibration} shows the results of the first test, here a problem with slow water flow was
identify, this was due to the sensor not being able to capture the change in water flow at low speeds. A series of
improvements in the code were made, like separating the code in the different tasks, to be able to capture this more 
accuratly but it was not possible, it was concluded that a higher precision sensor was needed but it was not possible to
get one in time for the project.

Figure \ref{fig:water-flow-sensor-response} shows the response of the water flow sensor when filling up the container,
the sensor was able to capture the change in water flow in less than 10 seconds, which was within the acceptable range
when thinking about fast common tasks like filling up a glass of water, anything below this speed might not be captured
by the sensor, i.e. opening the faucet to get a little stream of water.

\subsubsection{Temperature Sensors}

Testing the temperature sensors required two different tests, first the sensors were compared to a thermometer to check
the accuracy of the readings in a span of 12 hours, the results were satisfactory as the standard deviation was less
than 0.5 degrees Celsius. The second test was to check the response time of the sensors, this was done by placing one
sensor in a glass full of ice and the other in a glass full of boiling water, figure 
\ref{tab:temperature-sensors-calibration} shows the results of the calibration tests for the temperature sensors.


Figure \ref{fig:temp-sensor-response} shows the change in temperature when the sensors were submerged, once the
temperature reached the maximum and minimum values the sensors were swapped to check the response time, it was less than
a minute which was within the acceptable range for the application, there are no changes so drastic in temperature
inside or outside a room.

% \begin{itemize}
%     \item Hardware Testing: make sure the hardware components are working properly.
%     \item Unit Testing: unit tests for the code running the API.
%     \item Integration Testing: integration tests between each system layer.
%     \item System Testing: end-to-end testing (including interaction with host dashboard) using simulated stays.
%     \item Regression Testing: Github Actions integrated into the develpment process to make sure nothing breaks when changes were introduced. This included linting the code.
%     \item User Testing: A small group of users (guests and hosts) tested the system and completed a survey to collect the result of their experiences using the application.
% \end{itemize}

% Introduction
% Describe your methodology: provide details
% Present your results
% Discuss your findings
% Address limitations
% Relate back to literature review
% Explain your experiments
% Assessment of experiments
% End result: software itself
% Conclude with implications of future work

% \section{Evaluation}

% * Evaluation and critical evaluation of the results including strong and weak points, lessons learnt, and design decisions.
% \begin{itemize}
% 	\item Consider what you would do differently, are there ways in which the project could be improved or extended?
% \end{itemize}